Efficient Coalition Formation for Web Services

### 2013-03-04 notes/coop.tex
Changes

>>>>

Any convex game is necessarily superadditive: if a game G = (N, v) is convex, and C and D are two disjoint subsets of N, then we have (here we use our assumption that v(.) = 0). However, the converse is not always true, as illustrated
by the following example. 
Consider a game G = (N, v), where N = {1, 2, 3}, and v(C) = 1 if |C| . 2 and v(C) = 0 otherwise; this game is known as the 3-player majority game. It is easy to check that this game is superadditive.Onthe other hand, forC = {1, 2} andD = {2, 3},we have v(C) = v(D) = 1

### 2013-03-04 papers/coalition/coalition.tex
Changes

>>>>

\subsubsection{$\epsilon-Core$}
If core set is not empty, it means no coalition of players can gain anything by deviating, it is the strongest stable condition. An outcome would be unstable if a coalition can benefit even by a small amount from deviating. This is a strong requirement. In some situations, deciations can be costly or agents may have some loyatly to their coalitions or even it can be computationaly intractable to find those small benefits. It would only make sense for a coalition to deviate if the gain from a deviation exceeded a particular cost for example the costs of deviation. $\epsilon-Core$ relaxes the notion of the core, and only require that no coalition can benefit significantly or within a constant ammount($\epsilon$) by deviating.

\begin{equation}\label{eq:core}
\forall S \subseteq N, \sum_{x_i \in S} x_i \geq v(S) - \epsilon
\end{equation}
